\Large{Holier Than Thou? No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2023-01-04 ms/adult.tex
Update adult.tex

\section*{Measuring Pornographic Content}
We code pornographic content at the domain level. Our main analysis depends on the domain classifications that come with YouGov data. We code domains that YouGov categorizes as ``Adult'' as porn sites. These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com). A fraction of web browsing activity, approximately 84k or 1.3 percent, are to porn sites. See \cref{fig:top25_adult} and \cref{fig:top25_nonadult} for the top visited domains. Certain domains are not predominately for porn consumption and we remove these from the classification of porn sites. For instance, urbandictionary.com and 4chan.org are ``Adult'' but not classified as porn site.\footnote{We use the \texttt{forestplot} \citep{forestplot} and \texttt{tableone} \citep{tableone} packages to tabulate key descriptive figures.} \footnote{We manually check the top adult domains in our sample to remove obvious false positives of porn sites. Generally, if there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a porn site.}

@@

\subsection*{Consumption of Pornography}
Only about 32 percent of the respondents consumed pornography online during the sample period. The average consumer of pornography online spent approximately 230 minutes (standard deviation of 576 minutes). The consumption of pornography was highly concentrated among a few sites with ten most frequented pornography sites receiving more than 12 times the traffic to all other porn sites  (approximately 109 minutes vs. 9 minutes, see \cref{fig:concentration_porn_consumption}). Close to 80 percent of the traffic to pornographic sites is concentrated in just one pornographic site. Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male.

\subsection*{Partisan Differences in Consumption of Pornography Online}
%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

@@

Our primary dependent variables of interest are: total time spent on pornographic sites and the proportion of time spent on pornographic sites. (In \ref{si:visits}, we show similar analysis for visits.)

Given the skew in the data, we ran a quantile regression, regressing the duration on party. As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, there are no significant differences in consumption of pornographic content between the parties. To account for the possibility that these non-differences may be a result of confounding demographic differences between the parties, we control for immutable characteristics like age and gender to see if that adjustment changes the picture much. \cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification. We use these variables in our analyses of pornography consumption below. Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}.

@@

Consumption of pornography has been attributed to a variety of ills. It is also considered problematic from a religious perspective. Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}}. The Internet has dramatically increased access to pornography. This leads to the concern that pornography consumption has become very widespread. Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little or none.

>>>>

\section*{Measuring Pornographic Content}
We code pornographic content at the domain level. Our main analysis depends on the domain classifications that come with YouGov data. We code domains that YouGov categorizes as ``Adult'' as pornographic sites. These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com). Yougoc classifies certain domains as 'Adult' that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org . Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We use the \texttt{forestplot} \citep{forestplot} and \texttt{tableone} \citep{tableone} packages to tabulate key descriptive figures.}, we manually check the top adult domains to remove such sites. If there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a pornographic.

@@

\subsection*{Consumption of Pornography}
Across all respondents, only a small fraction of the web browsing visits, approximately 84,000 visits or 1.3 percent, are to pornographic sites. And these visits are concentrated among a few people. Only about 32 percent of the respondents consumed pornography online during the sample period. The average consumer of pornography online spent approximately 230 minutes (standard deviation of 576 minutes).

The consumption of pornography is also highly concentrated among a few sites, with ten most frequented pornography sites receiving more than 12 times the traffic to all other porn sites  (approximately 109 minutes vs. 9 minutes, see \cref{fig:concentration_porn_consumption}). Close to 80 percent of the traffic to pornographic sites is to just one pornographic site. Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male \cref{fig:} %TODO

\subsection*{Partisan Differences in Consumption of Pornography Online}
Our primary dependent variables of interest are: total time spent on pornographic sites and the proportion of time spent on pornographic sites. (In \ref{si:visits}, we show similar analysis for visits. The upshot is that the key conclusions are unaffected.)

Given the skew in the data, we ran a quantile regression, regressing the duration on party. As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, there are no significant differences in consumption of pornographic content between the parties. To account for the possibility that this may be a result of confounding demographic differences between the parties, we control for immutable characteristics like age and gender. (\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below. Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}. 
%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\caption{Quantile Estimates--Hours Spent on Porn Sites by Party}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours individuals in our sample spent on porn sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

@@

@@

Consumption of pornography has been attributed to a variety of ills. It is also considered problematic from a religious perspective. For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}}. The Internet has dramatically increased access to pornography. This has led to the concern that pornography consumption has become very widespread and extensive. Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little or none.
